HO unification from object language to meta language

### 2024-03-29 paper/main.tex
update elpi printe + some tex

\begin{gather}
\lambda x y.F \appsep y \appsep x = \lambda x y.x \label{eq:unif-eta1}\\
\lambda x. f \appsep (F \appsep x) \appsep x = f \appsep (\lambda y.y) \label{eq:unif-eta2}
\end{gather}
Note that here $F$ is used with different arities, moreover
in the second problem the left hand side happens to be an
eta expansion (of $f (\lambda y.y)$) only after we discover (at run time)
that $F = \lambda x\lambda y.y$ (i.e. that $F$ discards the $x$ argument).
Both problems are addressed in the next section.

@@

In \cref{sec:basic-comp-limitations}, we have given two unification problems to
be run one after the other. In the following table we present the entry problem,
its compiled version, with the corresponding list of mapping and links.
%
\printAll
  {{\elpiIn{flam x\flam y\fapp[fuva F,y,x] = flam x\flam y\x},
    \elpiIn{flam x\fapp[fcon"f", fapp[fuva F, x], x] = fapp[fcon"f", flam x\x]}}}
  {{X = \lambda x.\lambda y.x, Z = f\appsep(\lambda x.x)}}
  {{\mapping{F}{G}{1}, \mapping{F}{H}{2}}}
  {{\linketaM{x}{Y_{x}}{\lambda y.H_{y~x}},
    \linketaM{\phantx}{X}{\lambda x.Y_{x}},
    \linketaM{\phantx}{Z}{\lambda x.f \appsep G_{x}~x}}}

>>>>

\begin{gather}
\lambda x y.F \appsep y \appsep x = \lambda x y.x \label{eq:unif-eta1}\\
\lambda x. f \appsep (F \appsep x) \appsep x = G \label{eq:unif-eta2}
% \lambda x. f \appsep (F \appsep x) \appsep x = f \appsep (\lambda y.y) \label{eq:unif-eta2}
\end{gather}
Note that here $F$ is used with different arities, moreover
in the second problem the left hand side happens to be an
eta expansion (of $f (\lambda y.y)$) only after we discover (at run time)
that $F = \lambda x\lambda y.y$ (i.e. that $F$ discards the $x$ argument).
Both problems are addressed in the next section.

@@

In \cref{sec:basic-comp-limitations}, we have given two unification problems to
be run one after the other. In the following table we present the entry problem,
its compiled version, with the corresponding list of mapping and links.
%
\printAll
  {{\elpiIn{flam x\ flam y\ fapp [fuva X, y, x] == flam x\ flam y\ x},
    \elpiIn{flam x\ fapp [fcon"f", fapp [fuva X, x], x] == fuva Y}}}
  {{E0 == \lambda x.\lambda y.x,
    E3 == E5}}
  {{\mapping{Y}{E5}{0},
    \mapping{X}{E2}{2}}}
  {{\linketaM{c0}{E4_{c0}}{\lambda x.E2_{c0 x}},
    \linketaM{}{E3}{\lambda x.(f~E4_{x}~x)},
    \linketaM{}{E0}{\lambda x.E1_{x}},
    \linketaM{c0}{E1_{c0}}{\lambda x.E2_{x c0}}}}
